---
title: "Session 2: Problem Set"
author: Solution
date: "`r format(Sys.time(), '%d %B %Y')`"
output: 
  html_document:
    keep_md: false
    theme: yeti
    highlight: textmate
    code_folding: show
    toc: yes
    toc_depth: 4
    toc_float: yes
# Uncomment below to produce .pdf
#   pdf_document:
#     latex_engine: xelatex
#     keep_tex: false ## Change to true if want keep intermediate .tex file
#     toc: true
#     toc_depth: 3
#     dev: cairo_pdf
# knit: (function(inputFile, encoding) {
#  rmarkdown::render(inputFile, encoding = encoding,
#  output_format = 'all')
#  })
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

```{css echo=FALSE}
h1  {
  margin-top: 1em;
  margin-bottom: 1em;
}

h4  {
  margin-top: 1em;
  margin-bottom: 1em;
}
``` 

# Task 1

Specify a vector with numeric elements 1 and 3 and a character element "c".

What type will the resulting object be?

Check your intuition with R.

```{r}
x <- c(1,3,"c")
typeof(x)
```

# Task 2

Create a named list containing a data frame, a character vector and a list. Access the 
first element of the first element and the second element.

```{r}
# One solution:

z <- list(df = data.frame(x = c(2, 2), y = c("a", "b")),
          g = "c", 
          f = list(1, 2)
)

z$df[1]
z[[2]]
  
```

# Task 3
 
Assign the name "x" to an integer vector from 1 to 10. 

Create a logical vector "z" whose elements store whether x is greater than 2 and less than 8.

Compute the number of times the above condition is true (use `sum()`).

```{r}

x <- c(1:10)
x

z <- x > 2 & x < 8
z

sum(z)

sum(x > 2 & x < 8)
```


# Task 4

Given the data frame below, create a new column called "c" that contains the 
product of "a" and "b". Do this using `$` and `[` indexing (and maybe `names()`).
Remember, data frames are (special) lists! 


```{r}
df <- data.frame(
  a = c(1,1,2,3,4),
  b = c(3,2,2,4,5)
)

```

Your solution:

```{r}
df$c <- df$a * df$b

#Or

df["c"] <- df["b"] * df["a"]
```

# Task 5

In this task, you will learn a few important functions in base R.

#### 1. Sequences

Often, you want to create sequences of objects.

You can do so using the `rep()` function:

```{r}
x <- c(1,2,3)
rep(x, 3)

rep(x, each = 3)
```

Another way of creating sequences is `seq()`:

```{r}
seq(1, 5)
1:5
seq(1,5, by = 2)
```

#### 2. Manipulating Strings

You should also know some basic string manipulations from the beginning.

With `paste()` you can concatenate strings:

```{r}
x <- "a"

paste(x, 3)

paste(3, x)

paste(3, x, sep = "")

```

Can you spot the difference to `paste0()`?

```{r}
paste0(3, x)
```

#### 3. Classic (math) functions

Some very basic (math) functions: `sqrt()`, `exp()`, `log()`, `abs()`, `sum()`, `max()`, `min()`,
`length()` (length of an r object).

#### TASK:

Create a character vector with 20 elements: "1st element", "2nd element", 
"3rd element", "4th element", etc.

```{r}
chr <- paste0(1:20, c("st", "nd", "rd", rep("th", 17)))
chr <- paste(chr, "element")
chr
```

# Task 6

Write a function to compute the mean of a vector. Of course, without using the 
`mean()` function.

Define a vector you want to test your function on and specify the expected result:
```{r}
x <- c(1,2,3,4,5)
mean(x)
```

Write the function and test it:

```{r}
mean_fun <- function(x) {
  sum(x) / length(x)
}

mean_fun(x)
```