---
title: "Session 5: Data Viz Challenge"
subtitle: Solution
author: Your Name
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    keep_md: false
    code_folding: show
    theme: yeti
    highlight: textmate
    toc: yes
    toc_depth: 4
    toc_float: yes
# Uncomment below to produce .pdf
#   pdf_document:
#     latex_engine: xelatex
#     keep_tex: false ## Change to true if want keep intermediate .tex file
#     toc: true
#     toc_depth: 3
#     dev: cairo_pdf
# knit: (function(inputFile, encoding) {
#  rmarkdown::render(inputFile, encoding = encoding,
#  output_format = 'all')
#  })
---

```{r setup, include=FALSE}
# install package management tool pacman
# install.packages("pacman")

pacman::p_load(
  tidyverse,
  rio,
  modelsummary,
  patchwork,
  hrbrthemes,
  extrafont,
  RColorBrewer,
  here
)

knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

# Data Viz Challenge


```{r}
whogov <- import(here("Data", "WhoGov_crosssectional_V1.2.csv"))
```

Since data visualization is about creativity and just trying things out,
we will take a different approach in this problem set. 

Together with your group you will work on the [WhoGov](https://politicscentre.nuffield.ox.ac.uk/whogov-dataset/) data set. 
It provides information on governing elites. 

1. **Everyone on her/his own (5min):** Skim the [codebook](https://politicscentre.nuffield.ox.ac.uk/media/4117/whogov_codebook.pdf)
part **B**. We will **only use the cross-sectional data**.

2. **Together in your group (10min):** Discuss the data and agree on something
interesting you want to visualize. 

3. **Everyone on her/his own (30mins):** Implement the visualization you agreed
 upon in R. Tipp: You can use all the links and pointers from the slides or google
 when you are stuck!

4. **Together in your group (15mins):** Share your versions with your group. Pick the best and fine-tune it together. If
you like multiple versions, combine them into one plot/data story.


Back in the plenum, we will pick a winner!

Criteria:

- Is it a truthful display of the data?
- Is it functional?
- Is it pretty?
- Is it insightful?


# An exemplary "Solution"

Visualizing the share of female ministers over time by system type.

```{r, fig.width = 12, fig.height = 5}

# Define a ggplot theme

extrafont::loadfonts() # You must download and install IBM Plex from google fonts and register it with extrafont. Consult the package doc.

plex <- theme_ipsum() +
  theme(
    text = element_text(colour = "#415564", family = "IBM Plex Sans"),
    plot.title = element_text(colour = "#415564", family = "IBM Plex Sans"),
    plot.subtitle = element_text(colour = "#415564", family = "IBM Plex Sans"),
    plot.background = element_rect(fill = "#ffffff", color = "#ffffff"),
    panel.border = element_blank(),
    strip.text = element_text(colour = "#415564"),
    axis.text = element_text(colour = "#415564"),
    axis.title = element_text(colour = "#415564")
  )

theme_set(plex)


# Create a crosstab of the system_category and arrange by n

whogov %>%
  count(system_category) %>%
  arrange(n)

# Add a variable "regime_type" that takes on the value "democratic" if system_category
# contains the string "democ", "Dictatorship" if "dict", and "Other" otherwise.

whogov <- whogov %>%
  mutate(regime_type = case_when(
    stringr::str_detect(system_category, "dict") ~ "Dictatorship",
    stringr::str_detect(system_category, "democ") ~ "Democracy",
    TRUE ~ "Other"
  ))

# Create a crosstab of the system_category and regime_type

whogov %>%
  count(system_category, regime_type) %>%
  arrange(n)


plot_table <- whogov %>%
  mutate(share_fem_min = n_female_minister / n_minister) %>%
  group_by(year, regime_type) %>%
  summarise(avg_share_fem_minister = mean(share_fem_min, na.rm = TRUE)) %>%
  filter(regime_type != "Other") 
  
ggplot(plot_table, aes(x = year, y = avg_share_fem_minister, color = regime_type)) +
  geom_line() +
  geom_line(size = 1) +
  scale_colour_brewer(palette = "Dark2") +
  scale_x_continuous(breaks = seq(1960, 2020, 10)) +
  labs(
    x = "\nYear",
    y = "Share of \nFemale Ministers",
    color = "Regime Type (excluding 'Other')",
    title = "Share of Female Ministers in Democracies and Dictatorships over Time\n",
    caption = "Data from WhoGov (Nyrup/Bramwell 2021)."
  ) +
  theme(axis.title.y = element_text(angle = 0)) # rotate y axis label.

```
