---
title: "Session 6: Problem Set"
subtitle: Writing Functions
author: Solution
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    keep_md: false
    code_folding: show
    theme: yeti
    highlight: textmate
    toc: yes
    toc_depth: 4
    toc_float: yes
# Uncomment below to produce .pdf
#   pdf_document:
#     latex_engine: xelatex
#     keep_tex: false ## Change to true if want keep intermediate .tex file
#     toc: true
#     toc_depth: 3
#     dev: cairo_pdf
# knit: (function(inputFile, encoding) {
#  rmarkdown::render(inputFile, encoding = encoding,
#  output_format = 'all')
#  })
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

pacman::p_load(
  tidyverse,
  palmerpenguins,
  purrr
)

```


# Task 1

Take the following vector:

```{r}
x <- c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10)
```

Write a function that takes x as an argument and computes the sum of the elements 
in the vector using a `for` loop. Test it against the `sum()` function.

```{r}
sum_for <- function(x) {
  sum <- 0
  for (i in 1:length(x)) {
    sum <- sum + x[i]
  }
  return(sum)
}
  
sum_for(x)

sum(x)
```


# Task 2

We now turn towards a relatively easy problem that is often asked as a warm-up in coding interviews.

> Write a function that takes an integer number as an argument and puts out the word
"fizz" or "buzz" up to that integer. If an integer is divisible by 3, the function
should put out "fizz". If it is divisible by 5, the function should put out "buzz". If
it is divisible by both 3 and 5, the function should put out "fizzbuzz". If none of the
above holds true, the function should simply return the integer as a string.

In a first step, do this using a `for` loop and `if` statements. 
If you do not provide an integer number, the function should throw a meaningfull error message.

Tip: remember the modulo operator! 

```{r, error = TRUE}

fizzbuzz <- function(int = NULL) {
  
  if (is.numeric(int) == FALSE) {
    stop("Please provide an integer number.")
  }
  else if (int %% 1 != 0) {
    stop("Please provide an integer number.")
  }
  else {

  output <- vector(mode = "integer", length(1:int))

  for (i in 1:int) {
    if (i %% 3 == 0 && i %% 5 == 0) {
      output[i] <- "fizzbuzz"
    }
    else if (i %% 3 == 0) {
      output[i] <- "fizz"
    }
    else if (i %% 5 == 0) {
      output[i] <- "buzz"
    }
    else {
      output[i] <- i
    }
  }
  return(output)
  }
}

fizzbuzz(50)
fizzbuzz("3")
fizzbuzz(3.3)
fizzbuzz(TRUE)

```


# Task 3

Use `map()` from the `purrr` package to apply the `class()` and `typeof()` function
to each column of the palmerpenguins package.

```{r}
penguins %>% map(typeof)

penguins %>% map_chr(typeof)
penguins %>% map_chr(class)
```


ADVANCED TASK (skip if you are stuck):

Use `map_df` to compute a data frame consisting of variables showing the class and type 
of each column of the penguins data and a variable storing the column names of the penguins data.

Tip: You need to use `data.frame()` inside `map_df()` and create the variable you 
want inside this `data.frame()` call. Further, look into 
the `.id` argument of map to get the column names of the penguin data set.

```{r}

# Compare

penguins %>% map(~ data.frame(
  type = typeof(.x),
  class = class(.x)
),
.id = "variable"
)

# to

penguins %>% map_df(~ data.frame(
  type = typeof(.x),
  class = class(.x)
),
.id = "variable"
)

```

# Task 4

Take the function you defined in Task 2 and rewrite it such that it takes a vector 
of integers instead and works with `purrr::map_chr()`.

```{r}
fizzbuzz <- function(int = NULL) {
  if (is.numeric(int) == FALSE) {
    stop("Please provide an integer number.")
  }
  else if (int %% 1 != 0) {
    stop("Please provide an integer number.")
  }
  else {
      if (int %% 3 == 0 && int %% 5 == 0) {
        "fizzbuzz"
      }
      else if (int %% 3 == 0) {
        "fizz"
      }
      else if (int %% 5 == 0) {
        "buzz"
      }
      else {
       int
      }
  }
}

purrr::map_chr(1:50, fizzbuzz)

```
