---
title: "Session 3: Problem Set"
subtitle: Data Wrangling I
author: Your Name
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    keep_md: false
    code_folding: show
    theme: yeti
    highlight: textmate
    toc: yes
    toc_depth: 4
    toc_float: yes
# Uncomment below to produce .pdf
#   pdf_document:
#     latex_engine: xelatex
#     keep_tex: false ## Change to true if want keep intermediate .tex file
#     toc: true
#     toc_depth: 3
#     dev: cairo_pdf
# knit: (function(inputFile, encoding) {
#  rmarkdown::render(inputFile, encoding = encoding,
#  output_format = 'all')
#  })
---


```{r setup, include=FALSE}
# install package management tool pacman
# install.packages("pacman")

pacman::p_load(
  tidyverse,
  rio,
  modelsummary,
  knitr,
  here
)

```


```{r, include=FALSE}

knitr::opts_knit$set(root.dir = normalizePath('../'))
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```


```{r}
# The .csv would've had 200mb; .parquet is under  1mb. The power of compression.
unvotes <- rio::import(here("Data", "unvotes.parquet"))

```

# Data Wrangling UN Votes

In this problem set, we will use data from the [unvotes](https://github.com/dgrtwo/unvotes)
package. It contains data for all countries voting history in the general assembly.

Here is a description of the data set:

| variable      | description                                                                                                                                                              |
|---------------|--------------------------------------------------------------------------------------------------------------------------------------------------------------------------|
| rcid          | The roll call id; used to join with un_votes and un_roll_call_issues                                                                                                     |
| country       | Country name, by official English short name                                                                                                                             |
| country_code  | 2-character ISO country code                                                                                                                                             |
| vote          | Vote result as a factor of yes/abstain/no                                                                                                                                |
| session       | Session number. The UN holds one session per year; these started in 1946                                                                                                 |
| importantvote | Whether the vote was classified as important by the  U.S. State Department report "Voting Practices in the United Nations".  These classifications began with session 39 |
| date          | Date of the vote, as a Date vector                                                                                                                                       |
| unres         | Resolution code                                                                                                                                                          |
| amend         | Whether the vote was on an amendment; coded only until 1985                                                                                                              |
| para          | Whether the vote was only on a paragraph and not a resolution; coded only until 1985                                                                                     |
| short         | Short description                                                                                                                                                        |
| descr         | Longer description                                                                                                                                                       |
| short_name    | Two-letter issue codes                                                                                                                                                   |
| issue         | Descriptive issue name, 6 issues                                                                                                                                                   |

Source: [tidytuesday](https://github.com/rfordatascience/tidytuesday/blob/master/data/2021/2021-03-23/readme.md).

# Task 1

Familiarize yourself with the data. What's each variable's type/class?

```{r}

```

What is the level of observation of this data set?

Is this data set tidy?

# Task 2

## a)

With
```{r}
datasummary_skim(unvotes$issue, type = "categorical")
```
you get a quick summary for the categorical issue variable.

However, as each `rcid` occurs multiple times for each country, the issues are,
of course, also repeatedly present in our data.

What we want is a **sorted** table for the distribution of our issue variable 
over all roll calls.

Create such table/tibble/data frame using **only** tidyverse verbs/functions (scroll to the bottom of this document if you need a hint).

```{r}

```

## b) 

Which issue category has the highest share of important votes?

```{r}

```

# Task 3


## a) 

Add variables that show, for each country, the number and share of "yes", "no", and "abstain" votes, 
pooled over all years. Additionally, put out a tibble/data frame with one 
row for each country and these new variables. 

```{r}

```

## b) 

Calculate, for each country and issue, the number and share of "yes" votes but 
only for "important votes" and for security council's [permanent members](https://www.un.org/securitycouncil/content/current-members). The output should have 30 rows.

```{r}

```


## c) 

Get the years with the highest and lowest share of "yes" votes for 
each country.


```{r}

```


# Hints:

Task 2a: `distinct()` may be helpful here!

Task 2b: Check out the arguments of `distinct()`!