---
title: "Session 5: Data Viz Challenge"
subtitle: Data Viz Challenge
author: Your Name
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    keep_md: false
    code_folding: show
    theme: yeti
    highlight: textmate
    toc: yes
    toc_depth: 4
    toc_float: yes
# Uncomment below to produce .pdf
#   pdf_document:
#     latex_engine: xelatex
#     keep_tex: false ## Change to true if want keep intermediate .tex file
#     toc: true
#     toc_depth: 3
#     dev: cairo_pdf
# knit: (function(inputFile, encoding) {
#  rmarkdown::render(inputFile, encoding = encoding,
#  output_format = 'all')
#  })
---

```{r setup, include=FALSE}
# install package management tool pacman
# install.packages("pacman")

pacman::p_load(
  tidyverse,
  rio,
  modelsummary,
  patchwork,
  hrbrthemes,
  extrafont,
  RColorBrewer,
  knitr,
  here
)
```


```{r, include=FALSE}
knitr::opts_knit$set(root.dir = normalizePath('../'))
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```


```{r}
whogov <- import(here("Data", "WhoGov_crosssectional_V1.2.csv"))
```

# Data Viz Challenge

Since data visualization is about creativity and just trying things out,
we will take a different approach in this problem set. 

Together with your group you will work on the [WhoGov](https://politicscentre.nuffield.ox.ac.uk/whogov-dataset/) data set. 
It provides information on governing elites. 

1. **Everyone on her/his own (5min):** Skim the [codebook](https://politicscentre.nuffield.ox.ac.uk/media/4117/whogov_codebook.pdf)
part **B**. We will **only use the cross-sectional data**.

2. **Together in your group (10min):** Discuss the data and agree on something
interesting you want to visualize. 

3. **Everyone on her/his own (30mins):** Implement the visualization you agreed
 upon in R. Tipp: You can use all the links and pointers from the slides or google
 when you are stuck!

4. **Together in your group (15mins):** Share your versions with your group. Pick the best and fine-tune it together. 


Back in the plenum, we will pick a winner!

Criteria:

- Is it a truthful display of the data?
- Is it functional?
- Is it pretty?
- Is it insightful?


```{r}

```